\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}
 \geometry{
 margin=5mm,
 a4paper,
 left=20mm,
 top=20mm,
 right=20mm,
 bottom=20mm
 }
 
\title{resume}
\author{jnaman806 }
\date{February 2018}

\begin{document}
\noindent
\textbf{Naman Jain}\\
Department of Computer Science and Engineering\\
Indian Institute of Technology Kanpur, India\\
Email: namanj@iitk.ac.in\\
\hline
\hline 
\vspace{1em}
\noindent
\textit{This paragraph is brief about me.} I am Sophomore at IIT Kanpur who aspires to become data-scientist and is inclined towards research. I am interested in Competitive Programming.  Developing an algorithm and thinking in that way makes me feel wonderful. There are lot of things to do. And I can't list them all up here.
\vspace{1em}
\hline
\hline
\vspace{1em}
\noindent
\textbf{Education:}\\ \\
\begin{tabular}{|l|l|l|l|}
    \hline
    Matriculation & 2014 & Dyal Singh Public School & 10 CGPA\\
    \hline
    Intermediate &  2016 & Dyal Singh Public School & 50\\
    \hline
    BTech & 2016-Present & IIT Kanpur & 9.10\\
    \hline
\end{tabular}

\vspace{1em}
\noindent
\textbf{Course Details:}
\vspace{1em}\\
\begin{tabular}{|l|l|l|}
    \hline
    \textbf{Semester} & \textbf{Total Credits} & \textbf{Highlights} \\ \hline
    Aug 16 - Dec 16 & 52 & ESC101\\ \hline
    Jan 17 - Apr 17 & 53 & TA101\\   \hline
    Aug 17 - Dec 17 & 63 & CS201\\    \hline
    Jan 18 - Apr 18 & 57 & ESO207\\    \hline
\end{tabular}
\vspace{1em}

\noindent
\textbf{Skills:}
\vspace{1em}\\
\begin{tabular}{ll}
Computer Science &: OS, Machine Learning \\
Programming Skills &: C, C++, Python, Bash
\end{tabular}
\vspace{1em}

\noindent
\textbf{Projects:}
\begin{enumerate}
    \item \textbf{ACA Project:} Analysed various network technologies. Implemented PHP and mySQL to make web-app NamanCorp in which authorised user can login and update content while others may just visit site. Learnt about top 10 OWASP attacks and implemented few of them on DVWA.Analysed basics of cryptography, specifically RSA Algorithm.
    \item \textbf{Code.Fun.Do} Made a realtime android chat application. The app was made on Android Studio with frontend in XML and Firebase which is a realtime database, on the backend.The app was successfully submitted.
\end{enumerate}

\noindent
\textbf{Awards and Achievements:}
\begin{itemize}
    \item [--] Rank 1 in JEE(Advanced)
    \item [--] Gold medal in Olympics
\end{itemize}

\noindent
\textbf{Hobbies:}
\begin{itemize}
    \item [--] Sports: Football, Table-Tennis
    \item [--] Music: Guitar, Keyboard
\end{itemize}
\end{document}